Linear stability analysis for \textit{monami} in a submerged sea grass bed

### 2015-06-19 Paper_JFM/grass.tex
Fix authors list

\definecolor{tableShade}{gray}{0.8}
% \title{\textit{Monami} as an oscillatory hydrodynamic instability in a submerged sea grass bed}
\title{Linear stability analysis for \textit{monami} in a submerged sea grass bed}
\author{Ravi Singh}
\affiliation{Brown University, Providence RI 02912 USA}
% \author{L. Mahadevan}
% \affiliation{Harvard University, Cambridge MA 02138 USA}
\author{M. M. Bandi}
\affiliation{OIST Graduate University, Okinawa 904-0495, Japan}
\author{Amala Mahadevan}
\affiliation{Woods Hole Oceanographic Institution, Woods Hole MA 02543 USA}
\author{Shreyas Mandre}
\affiliation{Brown University, Providence RI 02912 USA}

>>>>

\definecolor{tableShade}{gray}{0.8}
% \title{\textit{Monami} as an oscillatory hydrodynamic instability in a submerged sea grass bed}
\title{Linear stability analysis for \textit{monami} in a submerged sea grass bed}
\author{
Ravi Singh\aff{1}, 
M. M. Bandi\aff{2},
Amala Mahadevan\aff{3}
\and
Shreyas Mandre\aff{4}}
\affiliation{
\aff{1}Department of Physics, Brown University, Providence RI 02912 USA
\aff{2}OIST Graduate University, Okinawa 904-0495, Japan
\aff{3}Physical Oceanography, Woods Hole Oceanographic Institution, Woods Hole MA 02543 USA
\aff{4}School of Engineering, Brown University, Providence RI 02912 USA
}
